Water Management

### 2020-01-16 Paper/paper.tex
ChgIntro

Using dynamic programming...

>>>>

Using dynamic programming in combination with a stochastic simulation of the rainfall, we determined the optimal irrigation policy that maximizes the combined utility of farmers and citizens for a number of years $T$. 
The sequence of events for every period is displayed in figure x.

\subsubsection{Modification 1: Variation of the discount factor}

An theoretical explanation of the used concepts will be given in chapter x
